### 2016-06-16 Appendix.tex
up to RSymmetry

\subsection{Weyl basis and 2-spinor notation}\label{sec:2spinor_notation}
As representation of the $\gamma$-matrices the Weyl or chiral representation is chosen:
\begin{align}
&\gamma^\mu = \begin{pmatrix}
0 && \sigma^\mu\\
\overline{\sigma}^\mu && 0
\end{pmatrix} &&
\gamma_5 = \begin{pmatrix}
-\mathbbm{1}_2 && 0\\
0 && \mathbbm{1}_2
\end{pmatrix}
\end{align}
with
\begin{align}
&\sigma^\mu = \begin{pmatrix}
\mathbbm{1}_2 && \sigma^i
\end{pmatrix}, &&
\overline{\sigma}^\mu = \begin{pmatrix}
\mathbbm{1}_2 && -\sigma^i
\end{pmatrix},\label{eq:Pauli}
\end{align}
where $\sigma^i$ are the Pauli matrices and $\mathbbm{1}_n$ is the $n \times n$ unit matrix. The left and right handed projectors are then given by
\begin{align}
P_L = \frac{1}{2}(\mathbbm{1}_4 - \gamma_5)\begin{pmatrix}
\mathbbm{1}_2 && 0\\
0 && 0
\end{pmatrix} && 
P_R = \frac{1}{2}(\mathbbm{1}_4 + \gamma_5)\begin{pmatrix}
0 && 0\\
0 && \mathbbm{1}_2
\end{pmatrix}\label{eq:projectors}
\end{align}
The representation of generators of the Lorentz group on 4-spinor space are composed of the above matrices. Because of the block form of those it is not surprising that the representation on 4-spinor space is reducible to two representations on 2-spinor (Weyl spinor) spaces. It is therefore sensible to decompose a 4 spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis (eq. \ref{eq:projectors}) explain the names left and right handed Weyl spinors.}
\begin{align}
\Psi = \begin{pmatrix}
\psi_\alpha \\
\overline{\chi}^{\dot{\alpha}}
\end{pmatrix}
\end{align}
where $\alpha,\dot{\alpha} \in \left\{ 1,2 \right\}$. Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices. One distinguishes 4 different Weyl spinors:
\begin{align}
\psi^\alpha, \hspace{1cm} 
\overline{\psi}^{\dot{\alpha}} = (\psi^\alpha)^\ast, \hspace{1cm} \psi_\alpha = \epsilon_{\alpha\beta}\psi^\beta, \hspace{1cm} \mathrm{and} \hspace{1cm} \psi_{\dot{\alpha}} = \epsilon_{\dot{\alpha}\dot{\beta}}\psi^{\dot{\beta}} = (\psi_\alpha)^\ast,
\end{align}
where $^\ast$ denotes complex conjugation and indices are lowered with the antisymmetric $\epsilon_{\alpha\beta}$ ($\epsilon_{\dot{\alpha}\dot{\beta}}$), which obeys
\begin{align}
\epsilon^{\alpha\beta} = \epsilon_{\beta\alpha},\ \epsilon^{\dot{\alpha}\dot{\beta}} = \epsilon_{\dot{\beta}\dot{\alpha}} \hspace{3cm} \mathrm{and} \hspace{3cm} \epsilon_{12} = \epsilon_{\dot{1}\dot{2}}= 1.
\end{align}
By virtue of the antisymmetry of $\epsilon$ one finds the Lorentz invariant products:
\begin{align}
\psi\chi &:= \psi^\alpha\chi_\alpha = -\chi_\alpha\psi^\alpha = \chi^\alpha\psi_\alpha = \chi\psi,\nonumber\\
\overline{\psi}\overline{\chi} &:= \overline{\psi}_{\dot{\alpha}} \overline{\chi}^{\dot{\alpha}} = -\overline{\chi}^{\dot{\alpha}}\overline{\psi}_{\dot{\alpha}} = \overline{\chi}_{\dot{\alpha}}\overline{\psi}^{\dot{\alpha}} = \overline{\chi}\overline{\psi} \label{eq:Weylspinorproduct}
\end{align}
To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\sigma^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}. For the definition of the super algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
\begin{align}
\frac{1}{2}(\sigma^{\mu\nu})_\alpha^{\ \beta} := \frac{i}{4}(\sigma^\mu\overline{\sigma}^\nu - \sigma^\nu\overline{\sigma}^\mu)_\alpha^{\ \beta}\nonumber\\
\frac{1}{2}(\overline{\sigma}^{\mu\nu})^{\dot{\alpha}}_{\ \dot{\beta}} := \frac{i}{4}(\overline{\sigma}^\mu\sigma^\nu - \overline{\sigma}^\nu\sigma^\mu)^{\dot{\alpha}}_{\ \dot{\beta}}
\end{align}

@@

\subsection{Anticommuting numbers}\label{sec:AnticommNumbers}
Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary numbers.\\
They occur in superspace formalism in the form of 2 tuples, i.e. $\theta^\alpha$ with $\alpha=1,2$. The complex conjugate of this tuple is denoted with $\overline{\theta}^{\dot{\alpha}}$. 
Derivatives are defined by
\begin{align}
\partial^\alpha \theta_\beta := \frac{\partial}{\partial \theta_\alpha} \theta_\beta := \delta^\alpha_\beta \hspace{4cm} \partial_\alpha \theta^\beta := \frac{\partial}{\partial \theta^\alpha} \theta^\beta := \delta_\alpha^\beta\nonumber\\
\overline{\partial}^{\dot{\alpha}} \overline{\theta}_{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} \overline{\theta}_{\dot{\beta}} := \delta^{\dot{\alpha}}_{\dot{\beta}} \hspace{4cm} \overline{\partial}_{\dot{\alpha}} \overline{\theta}^{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} \overline{\theta}^{\dot{\beta}} := \delta_{\dot{\alpha}}^{\dot{\beta}}
\end{align}
whereby one needs to be cautious as these definitions imply
\begin{align}
\partial_\alpha = -\epsilon_{\alpha\beta}\partial^\beta \hspace{4cm} \partial_{\dot{\alpha}} = -\epsilon_{\dot{\alpha}\dot{\beta}}\partial^{\dot{\beta}}.
\end{align}
Integrals are defined by:
\begin{align}
\int\mathrm{d}\theta_\alpha\ (a+b \theta^\beta + c\theta^\beta \theta^\gamma) &:= b\delta_{\alpha}^{\beta} + c (\delta_\alpha^\beta \theta^\gamma - \delta_\alpha^\gamma \theta^\beta) \hspace{1cm} \mathrm{and} \nonumber\\
\int\mathrm{d}\theta_\alpha\ (a\overline{\theta}^{\dot{\beta}}) &:= (a\overline{\theta}^{\dot{\beta}}) \int\mathrm{d}\theta_\alpha\
\end{align}
where the first line mirrows the claim of translation invariance. One furthermore introduces the shortcuts
\begin{align}
\int \mathrm{d}\theta^2 &:= \int\frac{1}{4}\epsilon_{\alpha\beta} \mathrm{d}\theta^\alpha\mathrm{d}\theta^\beta, \hspace{1cm}
\int \mathrm{d}\overline{\theta}^2 := \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}}, \hspace{1cm} \mathrm{and} \nonumber\\
\int \mathrm{d}^4\theta &:= \int \mathrm{d}\theta^2\mathrm{d}\overline{\theta}^2.
\end{align}
For the definition of (anti-)chiral superfields and the field strength chiral superfields it proves useful to introduce supersymmetry (or chiral) covariant derivatives 
\begin{align}
&\mathcal{D}_\alpha := \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu && \mathcal{D}^{\dot{\alpha}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} - i(\overline{\sigma}^\mu\theta)^{\dot{\alpha}} \partial_\mu\nonumber\\
&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)^{\dot{\alpha}} \partial_\mu.
\end{align}
By construction they are supersymmetry invariant, i.e. they fulfill the following anticommutation relations with the supersymmetry generators from eq. \ref{eq:SUSYGen}:
\begin{align}
\left\{ Q_\alpha, \mathcal{D}_\beta \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{D}_\beta \right\} = \left\{ Q_\alpha, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = 0
\end{align}

>>>>

\subsection{Weyl basis and 2-spinor notation}\label{sec:2spinor_notation}
As representation of the $\gamma$-matrices the Weyl or chiral representation is chosen:
\begin{align}
&\gamma^\mu = \begin{pmatrix}
0 && \sigma^\mu\\
\overline{\sigma}^\mu && 0
\end{pmatrix} &&
\gamma_5 = \begin{pmatrix}
-\mathbbm{1}_2 && 0\\
0 && \mathbbm{1}_2
\end{pmatrix}
\end{align}
with
\begin{align}
&\sigma^\mu = \begin{pmatrix}
\mathbbm{1}_2 && \sigma^i
\end{pmatrix}, &&
\overline{\sigma}^\mu = \begin{pmatrix}
\mathbbm{1}_2 && -\sigma^i
\end{pmatrix},\label{eq:Pauli}
\end{align}
where $\sigma^i$ are the Pauli matrices and $\mathbbm{1}_n$ is the $n \times n$ unit matrix. The left and right handed projectors are then given by
\begin{align}
P_L = \frac{1}{2}(\mathbbm{1}_4 - \gamma_5)\begin{pmatrix}
\mathbbm{1}_2 && 0\\
0 && 0
\end{pmatrix} && 
P_R = \frac{1}{2}(\mathbbm{1}_4 + \gamma_5)\begin{pmatrix}
0 && 0\\
0 && \mathbbm{1}_2
\end{pmatrix}\label{eq:projectors}
\end{align}
The representation of generators of the Lorentz group on 4-spinor space are composed of the above matrices. Because of the block form of those it is not surprising that the representation on 4-spinor space is reducible to two representations on 2-spinor (Weyl spinor) spaces. It is therefore sensible to decompose a 4 spinor into a left and a right handed Weyl spinor\footnote{The projectors in the chiral basis (eq. \ref{eq:projectors}) explain the names left and right handed Weyl spinors.}
\begin{align}
\Psi = \begin{pmatrix}
\psi_\alpha \\
\overline{\chi}^{\dot{\alpha}}
\end{pmatrix}
\end{align}
where $\alpha,\dot{\alpha} \in \left\{ 1,2 \right\}$. Left handed Weyl spinors are labeled with undotted and right handed Weyl spinors with dotted indices. One distinguishes 4 different Weyl spinors:
\begin{align}
\psi^\alpha, \hspace{1cm} 
\overline{\psi}^{\dot{\alpha}} = (\psi^\alpha)^\ast, \hspace{1cm} \psi_\alpha = \epsilon_{\alpha\beta}\psi^\beta, \hspace{1cm} \mathrm{and} \hspace{1cm} \psi_{\dot{\alpha}} = \epsilon_{\dot{\alpha}\dot{\beta}}\psi^{\dot{\beta}} = (\psi_\alpha)^\ast,
\end{align}
where $^\ast$ denotes complex conjugation and indices are lowered with the antisymmetric $\epsilon_{\alpha\beta}$ ($\epsilon_{\dot{\alpha}\dot{\beta}}$), which obeys
\begin{align}
\epsilon^{\alpha\beta} = \epsilon_{\beta\alpha},\ \epsilon^{\dot{\alpha}\dot{\beta}} = \epsilon_{\dot{\beta}\dot{\alpha}} \hspace{3cm} \mathrm{and} \hspace{3cm} \epsilon_{12} = \epsilon_{\dot{1}\dot{2}}= 1.
\end{align}
By virtue of the antisymmetry of $\epsilon$ one finds the Lorentz invariant products:
\begin{align}
\psi\chi &:= \psi^\alpha\chi_\alpha = -\chi_\alpha\psi^\alpha = \chi^\alpha\psi_\alpha = \chi\psi,\nonumber\\
\overline{\psi}\overline{\chi} &:= \overline{\psi}_{\dot{\alpha}} \overline{\chi}^{\dot{\alpha}} = -\overline{\chi}^{\dot{\alpha}}\overline{\psi}_{\dot{\alpha}} = \overline{\chi}_{\dot{\alpha}}\overline{\psi}^{\dot{\alpha}} = \overline{\chi}\overline{\psi} \label{eq:Weylspinorproduct}
\end{align}
To make the index structure of the Pauli matrices explicit one writes $\sigma^\mu_{\alpha\dot{\alpha}}$ and $\overline{\sigma}^{\mu\dot{\alpha}\alpha}$ for the formulae in \ref{eq:Pauli}. For the definition of the supersymmetry algebra in section \ref{sec:SUSYalgebra} the representation of the generators of the Lorentz group on the left and right handed Weyl spinor space are introduced:
\begin{align}
\frac{1}{2}(\sigma^{\mu\nu})_\alpha^{\ \beta} := \frac{i}{4}(\sigma^\mu\overline{\sigma}^\nu - \sigma^\nu\overline{\sigma}^\mu)_\alpha^{\ \beta}\nonumber\\
\frac{1}{2}(\overline{\sigma}^{\mu\nu})^{\dot{\alpha}}_{\ \dot{\beta}} := \frac{i}{4}(\overline{\sigma}^\mu\sigma^\nu - \overline{\sigma}^\nu\sigma^\mu)^{\dot{\alpha}}_{\ \dot{\beta}}
\end{align}

@@

\subsection{Anticommuting numbers}\label{sec:AnticommNumbers}
Anticommuting numbers $\theta^\alpha$ are also referred to as Grassmann numbers and are defined by $\theta^\alpha\theta^\beta = -\theta^\beta\theta^\alpha$ and commute with ordinary numbers.\\
They occur in superspace formalism in the form of 2 tuples, i.e. $\theta^\alpha$ with $\alpha=1,2$. The complex conjugate of this tuple is denoted with $\overline{\theta}^{\dot{\alpha}}$. 
Derivatives are defined by
\begin{align}
\partial^\alpha \theta_\beta := \frac{\partial}{\partial \theta_\alpha} \theta_\beta := \delta^\alpha_\beta \hspace{4cm} \partial_\alpha \theta^\beta := \frac{\partial}{\partial \theta^\alpha} \theta^\beta := \delta_\alpha^\beta\nonumber\\
\overline{\partial}^{\dot{\alpha}} \overline{\theta}_{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} \overline{\theta}_{\dot{\beta}} := \delta^{\dot{\alpha}}_{\dot{\beta}} \hspace{4cm} \overline{\partial}_{\dot{\alpha}} \overline{\theta}^{\dot{\beta}} := \frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} \overline{\theta}^{\dot{\beta}} := \delta_{\dot{\alpha}}^{\dot{\beta}}
\end{align}
whereby one needs to be cautious as these definitions imply
\begin{align}
\partial_\alpha = -\epsilon_{\alpha\beta}\partial^\beta \hspace{4cm} \partial_{\dot{\alpha}} = -\epsilon_{\dot{\alpha}\dot{\beta}}\partial^{\dot{\beta}}.
\end{align}
Integrals are defined by:
\begin{align}
\int\mathrm{d}\theta_\alpha\ (a+b \theta^\beta + c\theta^\beta \theta^\gamma) &:= b\delta_{\alpha}^{\beta} + c (\delta_\alpha^\beta \theta^\gamma - \delta_\alpha^\gamma \theta^\beta) \hspace{1cm} \mathrm{and} \nonumber\\
\int\mathrm{d}\theta_\alpha\ (a\overline{\theta}^{\dot{\beta}}) &:= (a\overline{\theta}^{\dot{\beta}}) \int\mathrm{d}\theta_\alpha\
\end{align}
where the first line mirrows the claim of translation invariance. One furthermore introduces the shortcuts
\begin{align}
\int \mathrm{d}\theta^2 &:= \int\frac{1}{4}\epsilon_{\alpha\beta} \mathrm{d}\theta^\alpha\mathrm{d}\theta^\beta, \hspace{1cm}
\int \mathrm{d}\overline{\theta}^2 := \int\frac{1}{4}\epsilon_{\dot{\alpha}\dot{\beta}} \mathrm{d}\theta^{\dot{\alpha}}\mathrm{d}\theta^{\dot{\beta}}, \hspace{1cm} \mathrm{and} \nonumber\\
\int \mathrm{d}^4\theta &:= \int \mathrm{d}\theta^2\mathrm{d}\overline{\theta}^2.
\end{align}
For the definition of (anti-)chiral superfields and the field strength chiral superfields it proves useful to introduce supersymmetry (or chiral) covariant derivatives 
\begin{align}
&\mathcal{D}_\alpha := \frac{\partial}{\partial \theta^\alpha} - i(\sigma^\mu\overline{\theta})_\alpha\partial_\mu && \mathcal{D}^{\dot{\alpha}} := \frac{\partial}{\partial \overline{\theta}_{\dot{\alpha}}} - i(\overline{\sigma}^\mu\theta)^{\dot{\alpha}} \partial_\mu\nonumber\\
&D^\alpha := \epsilon^{\alpha\beta} D_\beta = -\frac{\partial}{\partial \theta_\alpha} + i(\overline{\theta} \overline{\sigma}^\mu)^\alpha \partial_\mu && \mathcal{D}_{\dot{\alpha}} := \epsilon_{\dot{\alpha}\dot{\beta}} \mathcal{D}^{\dot{\beta}} = -\frac{\partial}{\partial \overline{\theta}^{\dot{\alpha}}} + i(\sigma^\mu\theta)_{\dot{\alpha}} \partial_\mu.
\end{align}
By construction they are supersymmetry invariant, i.e. they fulfill the following anticommutation relations with the supersymmetry generators from eq. \ref{eq:SUSYGen}:
\begin{align}
\left\{ Q_\alpha, \mathcal{D}_\beta \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{D}_\beta \right\} = \left\{ Q_\alpha, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = \left\{ \overline{Q}_{\dot{\alpha}}, \mathcal{\mathcal{D}}_{\dot{\beta}} \right\} = 0
\end{align}
